---
title: "London House Price Analyse"
output: html_document
---
Combined the factors which influenced by the epidemic and the various characteristics of each London boroughs, this study not only attempts to provide insight on the impact on house prices caused by the pandemic of the different London boroughs, but also shows the individuals’ changed demand for the house.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Library Packages

Firstly, Let's library some packages which we will use in this work
```{r library}
library(tidyverse)
library(janitor)
library(plotly)
library(maptools)
library(RColorBrewer)
library(classInt)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(tmaptools)
library(ggplot2)
library(corrplot)
library(haven)
library(texreg)
library(dplyr) 
library(tidyr)
library(broom)
library(MASS)
library(car)
library(ggplot2)
library(GGally)
library(spdep)
library(sf)
library(sp)
library(lwgeom)
library(spData)
library(spatialreg)
library(Matrix)
library(spgwr)
```

## 2.Import Data 

Now Let's import the data and have quick look of the data
```{r import data}
hpa <- read_csv("house_price_analyse.csv")

head(hpa)

hpa_num <- dplyr :: select_if(hpa, is.numeric)
```

Load London borough shape file
```{r load London borough shape file}
Londonborough <- st_read("ESRI/London_Borough_Excluding_MHW.shp") 
        
st_transform(Londonborough, 27700)

Londonborough <- Londonborough[order(Londonborough$GSS_CODE), ]
head(Londonborough)
```

## 3.Preliminary Analysis

```{r summary the data}
#summary the data
summary(hpa)
```

plot the histgram of the house price year by year growth rate distribution
```{r histgram of house price year by year growth}
library(ggplot2)
# set up the basic histogram
gghist1 <- ggplot(hpa, 
                 aes(x = year_by_year_growth)) + 
  geom_histogram(color="black", 
                 fill="white")+
  labs(title="House Price Year by Year Growth Rate Distribution", 
       x="house price year by year growth", 
       y="Frequency")
gghist1
```

```{r histgram of sqrt house price year by year growth}
library(ggplot2)
# set up the basic histogram
gghist1 <- ggplot(hpa, 
                 aes(x = sqrt(year_by_year_growth))) + 
  geom_histogram(color="black", 
                 fill="white")+
  labs(title="House Price Year by Year Growth Rate Distribution", 
       x="house price year by year growth", 
       y="Frequency")
gghist1
```

```{r histgram of log house price year by year growth}
library(ggplot2)
# set up the basic histogram
gghist1 <- ggplot(hpa, 
                 aes(x = log(year_by_year_growth))) + 
  geom_histogram(color="black", 
                 fill="white")+
  labs(title="House Price Year by Year Growth Rate Distribution", 
       x="house price year by year growth", 
       y="Frequency")
gghist1
```

map the house price year by year growth rate
```{r map the house price growth rate}
#merge boundaries and data
hpa <- Londonborough%>%
  left_join(.,
            hpa, 
            by = c("GSS_CODE" = "area_code"))

hpa <- hpa[-1, ]
```


```{r map the data}
#let's map our dependent variable to see if the join has worked:
tmap_mode("view")
qtm(hpa, 
    fill = "year_by_year_growth", 
    borders = "black",  
    fill.palette = "Blues")
```

map the independent variables
```{r map the independent variables}
plot(hpa[10:15])
```

## 4. Explore the Correlation Between Datas

plot the correlation between the features
```{r plot the correlation between the features}
#create a dadaframe of the numeric datas
corrplot(cor(hpa_num))
```

ggpairs
```{r ggpairs}
ggpairs(hpa_num,axisLabels="none")
```

## 5. Build Linear Regression Models and Model Selection

# 5.1 Train models with original data

Build the models contains all the independent variables
```{r linear regression model with all of the independent variables}
lm.max <- lm(year_by_year_growth ~ ., data = hpa_num)
summary(lm.max)
```

# 5.2 Variable selection
Use Leaps to select the variables
```{r leaps lm.max}
library(leaps)

regsubsets.out <- regsubsets( year_by_year_growth ~ .,
                              data = hpa_num,
                              nbest = 1,
                              nvmax = NULL,
                              force.in = NULL, force.out = NULL,
                              method = 'exhaustive')
summary(regsubsets.out)
  
as.data.frame(summary(regsubsets.out)$outmat)
plot(regsubsets.out, scale='adjr2', main='Adjusted Rsq')
```

According to the results show above, "cases_per_1000000", "aver_num_of_open_space", and "still_eco_secure" are the top three variables which are more significant to the dependent variable. So let's build a model employed these tree variables and check the performance of the model.
```{r build new model based on the results showed above}
lm_sel <- lm(year_by_year_growth ~ cases_per_1000000 + aver_num_of_open_space + still_eco_secure, data = hpa_num)
summary(lm_sel)
```


```{r create new dataframe}
hpa_num <- hpa_num[,c(-2, -4, -7)]
hpa <- hpa[,c(-10, -12, -15)]
```


# 5.3 Make sure the model meet the linear regression assumptions
As we can see that the new model dose not perform so well. So our final selection is the lm_new.max.

1.the residuals are normally distributed
```{r plot the residuals}
#save the residuals into the datafram
lm_modeldata_new <- lm_sel %>%
  augment(., hpa_num)

#plot residuals
lm_modeldata_new%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
  geom_histogram() 
```

2.There is no multicolinearity among the independent variables
```{r}
vif(lm_sel)
```

3.Homoscedasticity
plot the residuals against the predicted values.
```{r}
par(mfrow=c(2,2))    #plot to 2 by 2 array
plot(lm_sel)
```

4. The residuals of the model are not correlated.(Check the standard autocorrelation)
```{r}
DW <- durbinWatsonTest(lm_sel)
tidy(DW)
```

## 6.Spatial Autocorrelation

create the new dataframe
```{r add residual to the dataframe}
#create a new data frame with the transformed data
hpa$lm_resids = lm_sel$residuals
```

map the residuals
```{r map the residuals}
tmap_mode("view")
qtm(hpa, 
    fill = "lm_resids", 
    borders = "black",  
    fill.palette = "-RdBu")
```


```{r calculate the centroids of all Wards in London}
#calculate the centroids of boroughs in London
coordsB <- hpa%>%
  st_centroid()%>%
  st_geometry()
plot(coordsB)
```

```{r generate weight matrix}
#queen's case
LB_nb <- hpa %>%
  poly2nb(., queen=T)

#nearest neighbours
knn_B1 <-coordsB %>%
  knearneigh(., k=3)
knn_B2 <-coordsB %>%
  knearneigh(., k=5)

LB_knn3 <- knn_B1 %>%
  knn2nb()
LB_knn5 <- knn_B2 %>%
  knn2nb()

```

```{r plot queen}
#plot them
plot(LB_nb, st_geometry(coordsB), col="red")
```

```{r plot knn3}
plot(LB_knn3, st_geometry(coordsB), col="blue")
```

```{r plot knn5}
plot(LB_knn5, st_geometry(coordsB), col="blue")
```

```{r create spatial weights matrices}
#create a spatial weights matrix object from these weights
LB_queens_weight <- LB_nb %>%
  nb2listw(., style="C")

LB.knn_3_weight <- LB_knn3 %>%
  nb2listw(., style="C")

LB.knn_5_weight <- LB_knn5 %>%
  nb2listw(., style="C")
```

```{r}
Queen <- hpa %>%
  st_drop_geometry()%>%
  dplyr::select(lm_resids)%>%
  pull()%>%
  moran.test(., LB_queens_weight)%>%
  tidy()
Queen
```

```{r moran test for knn3}
Nearest_neighbour1 <- hpa %>%
  st_drop_geometry()%>%
  dplyr::select(lm_resids)%>%
  pull()%>%
  moran.test(., LB.knn_3_weight)%>%
  tidy()
Nearest_neighbour1
```

```{r moran test for knn5}
Nearest_neighbour2 <- hpa %>%
  st_drop_geometry()%>%
  dplyr::select(lm_resids)%>%
  pull()%>%
  moran.test(., LB.knn_5_weight)%>%
  tidy()
Nearest_neighbour2
```

## 7.Spatial Regression Models

# 7.1 SLM

```{r slm_queen}
slm_queen <- lagsarlm(year_by_year_growth ~ cases_per_1000000 +
                        aver_num_of_open_space + still_eco_secure,
               data = hpa, 
               nb2listw(LB_nb, style="C"), 
               method = "eigen")

#what do the outputs show?
summary(slm_queen)
```

```{r}
hpa <- hpa %>%
  mutate(slm_queen_resids = residuals(slm_queen))

QueenMoran <- hpa %>%
  st_drop_geometry()%>%
  dplyr::select(slm_queen_resids)%>%
  pull()%>%
  moran.test(., LB_queens_weight)%>%
  tidy()

QueenMoran
```

# 7.2 SEM

```{r SEM}
sem_queen <- errorsarlm(year_by_year_growth ~ cases_per_1000000 +
                        aver_num_of_open_space + still_eco_secure,
               data = hpa, 
               nb2listw(LB_nb, style="C"), 
               method = "eigen")

summary(sem_queen)
```

# 7.3 SDM
```{r}
queen.listw <- LB_queens_weight
listw1 <-  queen.listw
```

# 7.4 Local Moran's I
```{r local moran I of year by year house growth}
localmi <- localmoran(hpa$year_by_year_growth, listw=listw1, alternative = "greater")
localmi
```

```{r add local moran I into the dataframe}
hpa$hpmi <- localmi[,1]
```

```{r plot the loca Moran I}
tmap_mode("view")
qtm(hpa, 
    fill = "hpmi", 
    borders = "black",  
    fill.palette = "Blues")
```

#7.5 GWR
```{r change the projector of hpa}
st_crs(hpa) = 27700
```

```{r change hpa in to shape file}
hpa <- hpa %>%
  as(., "Spatial")
```

```{r change the projector of spatial weight matrix}
st_crs(coordsB) = 2770
```

```{r change coordsB in to shape file}
coordsBSP <- coordsB %>%
  as(., "Spatial")
```

```{r calculate kernel bandwidth}
GWRbandwidth <- gwr.sel(year_by_year_growth ~ cases_per_1000000 +
                        aver_num_of_open_space + still_eco_secure,
                        data = hpa,
                        coords=coordsBSP,
                        adapt=T)
```

build GWR model
```{r build gwr model}
gwr.model = gwr(year_by_year_growth ~ cases_per_1000000 +
                        aver_num_of_open_space + still_eco_secure,
                        data = hpa,
                        coords=coordsBSP,
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
gwr.model
```

analyse the results of GWR
```{r create dataframe of gwr results}
results <- as.data.frame(gwr.model$SDF)
names(results)
```

```{r add coefficients to shape file}
hpa_gwr <- hpa 
hpa_gwr$coefcasesrate <- results$cases_per_1000000
hpa_gwr$coefaveros <- results$aver_num_of_open_space
hpa_gwr$coefeco <- results$still_eco_secure
hpa_gwr$localr <- results$localR2
```

run significance test
```{r significance test of "cases_per_1000000"}
#run the significance test
sigTest_cases = abs(gwr.model$SDF$"cases_per_1000000")-2 * gwr.model$SDF$"cases_per_1000000_se"

#store significance results
hpa_gwr$casesig = sigTest_cases
```

```{r significance test of "aver_num_of_open_space"}
#run the significance test
sigTest_aver = abs(gwr.model$SDF$"aver_num_of_open_space")-2 * gwr.model$SDF$"aver_num_of_open_space_se"


#store significance results
hpa_gwr$aversig = sigTest_aver
```

```{r significance test of "still_eco_secure"}
#run the significance test
sigTest_eco = abs(gwr.model$SDF$"still_eco_secure")-2 * gwr.model$SDF$"still_eco_secure_se"


#store significance results
hpa_gwr$ecosig = sigTest_eco
```

map the sdandard errors
```{r map of "cases_per_1000000" standard errors}
tm_shape(hpa_gwr) +
  tm_polygons(col = "casesig", 
              palette = "Blues",
              alpha = 0.6)
```

```{r map of "aver_num_of_open_space" standard errors}
tm_shape(hpa_gwr) +
  tm_polygons(col = "aversig", 
              palette = "Blues",
              alpha = 0.6)
```

```{r map of "still_eco_secure" standard errors}
tm_shape(hpa_gwr) +
  tm_polygons(col = "ecosig", 
              palette = "Reds", 
              alpha = 0.6)
```

